---
title: "Yamaha FZ6N Fuel Efficiency"
author: "P. Melloy"
date: "01/06/2021"
output: html_document
---

```{r libraries}
library(googlesheets4)
library(data.table)
library(ggplot2)
```

The data for logging refueling data is collected by a google form and saved to a google sheet.
I am using the package `googlesheets4` to import the data with `

```{r data}
# indicate no authorisation is needed for the read only link
gs4_deauth() 

# import data
fuel <- setDT(read_sheet("https://docs.google.com/spreadsheets/d/1yEOMwOPqYLhcliRsHKjOXYl3GJNIsdgHYhQwObVAioU/edit?usp=sharing"))

# remove Null list entries
for(i in seq_len(nrow(fuel))){
   if(is.null(fuel$`Servo Brand`[[i]])){
      cat(fuel$`Servo Brand`[[i]])
      fuel$`Servo Brand`[[i]] <- NA_character_
   }
}
fuel[,`Servo Brand` := unlist(`Servo Brand`)]


# save a copy of raw data
fwrite(fuel, "data/fuel_dat.csv")
```

I need to inspect the data for any issues to ensure it's integrety
```{r}
summary(fuel)

setnames(fuel,
         old = colnames(fuel),
         new = c("ts", "refuel_date", "octane", "refuel_L", "price", "km",
                 "highwayP", "brand","price_e10", "price_91", "price_95",
                 "price_98", "notes"))
```
All the data looks in the correct range

```{r}
fuel[ octane >100,ocatane := 94]
fuel[,octane := as.integer(octane)]
```


Create a column for fuel efficiency, liters per km
```{r vol_km}
fuel[,eff := refuel_L/km]
```

offset octane to line up with efficiency
```{r}
fuel[, octane := c(NA, fuel[1:(.N-1),octane])]
```

plot efficiency
```{r}
fuel %>%
   ggplot(aes(y = eff, x = factor(octane)))+
   geom_boxplot()
```

cost per km
```{r}
# offset price
fuel[, price := c(NA, fuel[1:(.N-1),price])]

fuel[, costKm := (refuel_L * price)/km]


fuel %>%
   ggplot(aes(y = costKm, x = factor(octane)))+
   geom_boxplot()

```

